A new machine-learning based prediction of survival in patients with end-stage liver disease

### 2022-08-09 analysis/article.Rmd
fix: add Thorsten's new affiliation

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thomas Berg:
        email: thomas.berg@medizin.uni-leipzig.de
        institute: KIMH
        correspondence: false
    - Adam Herber:
        email: adam.herber@medizin.uni-leipzig.de
        institute: KIMH
        correspondence: false
    - Daniel Seehofer:
        email: daniel.seehofer@medizin.uni-leipzig.de
        institute: KVTTG
        correspondence: false
    - Berend Isermann:
        email: berend.isermann@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KIMH: Section of Hepatology, Department of Gastroenterology and Rheumatology, University Hospital Leipzig, Liebigstr. 20, D-04103 Leipzig, Germany.
    - KVTTG: Department of Visceral, Transplantation, Vascular and Thoracic Surgery, University Hospital of Leipzig, Liebigstr. 20, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Str., D-17475 Greifswald, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'ameld.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'zlog.bib')`"
output:
  bookdown::html_document2:
    keep_md: true
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
  bookdown::word_document2:
    keep_md: true
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
      - --csl=pandoc/csl/vancouver.csl
---

>>>>

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thomas Berg:
        email: thomas.berg@medizin.uni-leipzig.de
        institute: KIMH
        correspondence: false
    - Adam Herber:
        email: adam.herber@medizin.uni-leipzig.de
        institute: KIMH
        correspondence: false
    - Daniel Seehofer:
        email: daniel.seehofer@medizin.uni-leipzig.de
        institute: KVTTG
        correspondence: false
    - Berend Isermann:
        email: berend.isermann@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: [ILM, ILMOWL]
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KIMH: Section of Hepatology, Department of Gastroenterology and Rheumatology, University Hospital Leipzig, Liebigstr. 20, D-04103 Leipzig, Germany.
    - KVTTG: Department of Visceral, Transplantation, Vascular and Thoracic Surgery, University Hospital of Leipzig, Liebigstr. 20, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Str., D-17475 Greifswald, Germany.
    - ILMOWL: Institute of Laboratory Medicine, Microbiology and Clinical Pathobiochemistry, University Hospital OWL, Hospital Lippe, Röntgenstr. 18, D-32756 Detmold, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'ameld.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'zlog.bib')`"
output:
  bookdown::html_document2:
    keep_md: true
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
  bookdown::word_document2:
    keep_md: true
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
      - --csl=pandoc/csl/vancouver.csl
---
